Parametrization of Invertible Resnets up to Homology Equivalence for Abelian Lie Groups

### 2020-04-03 llncs2e/paper77.tex
typo

We use invertible architectures, to demonstrate our hypothesis on a different lie Group from Euclidean space \citemain{NguyenAK19}. Our interpretation of a neural net is a continuous transformation, transferring invariant structures of the data in the input space to its deepest layer. Thus, it is capable to reconstruct the structure of the original space. This approach corresponds to the concept of homotopy equivalence \citemain{RubinsteinR08,YangY93}, which means that there is a continuous map $f: X \rightarrow Y$ and $g: Y \rightarrow X$, such that $f \circ g$ is homotopic to the identity $\text{Id}_Y$ and $g \circ f$ to $\text{Id}_X$. Thus, the spaces can be deformed continuously into one another. To do so, their homotopy groups must be equal. The fundamental group gives information about connected components which can be collapsed to a point by continuous functions, the first homotopy group about `holes' and the second about `cavities' and so forth. But homotopies are difficult to compute \citemain{klaus2004quick,hatcher2002algebraic}. Homology theory gives a remedy that guarantees an isomorphism between homotopy groups and homology groups under the conditions of Hurewicz's Theorem \citemain{klaus2004quick}. We use theoretical results from Lie theory and persistent homology theory to estimate how many dimensions of embedding are needed to represent the homology groups. Our paper is structured as follows:
\begin{itemize}
    \item In Sect. \ref{sec:manifoldassumption} we discuss the mathematical assumptions and recall the principles of smooth manifolds and Lie theory. In particular, we recall the decomposition of connected commutative Lie groups into $\mathbb{R}^p \times \mathbb{T}^q$.
    \item In Sect. \ref{sec:persistenthomology} we introduce to the theory of persistent homology, define persistence diagrams, persistence landscapes and confidence sets, in order to estimate homology groups despite noisy data. We use Künneth's theorem and derive how to count the homology groups of the input space.
    \item In Sect. \ref{sec:neuralnettheory} we explain the mathematical theory of neural nets and construct invertible deep neural nets to satisfy our assumptions. Resnets, which have a larger state space dimension, offer an architecture with a comparatively small number of parameters to dense nets.
    \item In Sect. \ref{sec:numericalexperiments} we validate our theory training autoencoders on the cifar10 and cifar100 datasets, isolating the innermost layer such that no residual connections bypass it on different embedding dimensions.
\end{itemize}

@@

\paragraph{Code} The code can be found at: \href{https://github.com/karhunenloeve/PHIA}{https://github.com/karhunenloeve/PHIA}.
%
%
%
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystylemain{splncs04}
\bibliographymain{biblio}
%
\newpage
\appendix
\section{Supplementary Material for Sect. \ref{sec:manifoldassumption}}
\label{a:mannilliegroup}
\subsection{Groups}
\label{a:groups}
\begin{definition}
A set $G$ together with a map $\mu: G \times G \rightarrow G$, $(x,y) \mapsto xy$ and an element $e = e_G$ is called group if the following conditions are fulfilled:
\begin{enumerate}
	\item[(1)] $(xy)z = x(yz)$ for all $x,y,z \in G$, thus the elements are associative,
	\item[(2)] $xe = ex = x$ for all $x \in G$, so there is a neutral element and
	\item[(3)] $\forall x \in G \; \exists \; x^{-1} \in G$, such that $xx^{-1} = x^{-1}x = e$. 
\end{enumerate}
\end{definition}

>>>>

We use invertible architectures, to demonstrate our hypothesis on a different Lie group from Euclidean space \citemain{NguyenAK19}. Our interpretation of a neural net is a continuous transformation, transferring invariant structures of the data in the input space to its deepest layer. Thus, it is capable to reconstruct the structure of the original space. This approach corresponds to the concept of homotopy equivalence \citemain{RubinsteinR08,YangY93}, which means that there is a continuous map $f: X \rightarrow Y$ and $g: Y \rightarrow X$, such that $f \circ g$ is homotopic to the identity $\text{Id}_Y$ and $g \circ f$ to $\text{Id}_X$. Thus, the spaces can be deformed continuously into one another. To do so, their homotopy groups must be equal. The fundamental group gives information about connected components which can be collapsed to a point by continuous functions, the first homotopy group about `holes' and the second about `cavities' and so forth. But homotopies are difficult to compute \citemain{klaus2004quick,hatcher2002algebraic}. Homology theory gives a remedy that guarantees an isomorphism between homotopy groups and homology groups under the conditions of Hurewicz's Theorem \citemain{klaus2004quick}. We use theoretical results from Lie theory and persistent homology theory to estimate how many dimensions of embedding are needed to represent the homology groups. Our paper is structured as follows:
\begin{itemize}
    \item In Sect. \ref{sec:manifoldassumption} we discuss the mathematical assumptions and recall the principles of smooth manifolds and Lie theory. In particular, we recall the decomposition of connected commutative Lie groups into $\mathbb{R}^p \times \mathbb{T}^q$.
    \item In Sect. \ref{sec:persistenthomology} we introduce to the theory of persistent homology, define persistence diagrams, persistence landscapes and confidence sets, in order to estimate homology groups despite noisy data. We use Künneth's theorem and derive how to count the homology groups of the input space.
    \item In Sect. \ref{sec:neuralnettheory} we explain the mathematical theory of neural nets and construct invertible deep neural nets to satisfy our assumptions. Resnets, which have a larger state space dimension, offer an architecture with a comparatively small number of parameters to dense nets.
    \item In Sect. \ref{sec:numericalexperiments} we validate our theory training autoencoders on the cifar10 and cifar100 datasets, isolating the innermost layer such that no residual connections bypass it on different embedding dimensions.
\end{itemize}

@@

\paragraph{Code} The code can be found at: \href{https://github.com/karhunenloeve/Irhe}{https://github.com/karhunenloeve/Irhe}.
%
%
%
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystylemain{splncs04}
\bibliographymain{biblio}
%
\newpage
\appendix
\section{Supplementary Material for Sect. \ref{sec:manifoldassumption}}
\label{a:mannilliegroup}
\subsection{Groups}
\label{a:groups}
\begin{definition}
A set $G$ together with a map $\mu: G \times G \rightarrow G$, $(x,y) \mapsto xy$ and an element $e = e_G$ is called group if the following conditions are fulfilled:
\begin{enumerate}
	\item[(1)] $(xy)z = x(yz)$ for all $x,y,z \in G$, thus the elements are associative,
	\item[(2)] $xe = ex = x$ for all $x \in G$, so there is a neutral element and
	\item[(3)] $\forall x \in G \; \exists \; x^{-1} \in G$, such that $xx^{-1} = x^{-1}x = e$. 
\end{enumerate}
\end{definition}
